### 2018-02-13 paper/algorithm.tex
Adds short description of file-sharing protocol
Also changes some notation from previous commit.

A user's devices, \(D_i\), uses the Device Swarm Protocol to coordinate 
themselves.
More specifically, the devices use this protocol to keep the swarm state up to 
date.
The swarm state contains:
\begin{itemize}
  \item A knowledge vector, \(K_i\), encoding a Markov chain to predict online 
    and offline patterns for the various devices to predict when and for how 
    long each device might be available before disappearing again.
  \item A table, \(F_i\times \powerset(D_i)\), mapping a user's files (\(F_i\)) 
    to its devices (\(D_i\)) that store a copy of it.
\end{itemize}

@@

All swarms participates in the Inter-Swarm Protocol to coordinate the global 
knowledge needed by the swarms to interact.
More specifically, the global knowledge contains:
\begin{itemize}
  \item A table, \(A\), of available devices.
  \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
    fixed-length strings of length \(\lambda\) to arbitrary-length strings.
\end{itemize}

@@

\dots

>>>>

A user's devices, \(D_i\), uses the Device Swarm Protocol to coordinate 
themselves.
More specifically, the devices use this protocol to keep the swarm state up to 
date.
The swarm state contains:
\begin{itemize}
  \item A knowledge vector, \(A_i\), encoding a Markov chain to predict online 
    and offline patterns for the various devices to predict when and for how 
    long each device might be available before disappearing again.
  \item A table, \(F_i = N_i\times \powerset(D_i)\), mapping a user's file names 
    (\(N_i\)) to its devices (\(D_i\)) that store a copy of that file.
\end{itemize}

@@

All swarms participates in the Inter-Swarm Protocol to coordinate the global 
knowledge needed by the swarms to interact.
More specifically, the global knowledge contains:
\begin{itemize}
  \item A table, \(R\), of devices available for routing.
  \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
    fixed-length strings of length \(\lambda\) to arbitrary-length strings.
\end{itemize}

@@

When Alice wants to transfer a file to Bob, she will find which devices have the 
file (from \(F_i\)), then predict when any of those devices will be available 
(from \(A_i\)).
Then she will construct a probabilistic onion route with her devices as the 
destinations.
She will encrypt this route for Bob and transfer it to him, who now can use the 
onion route to fetch the file.
